---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# traj

<!-- badges: start -->
[![R-CMD-check](https://github.com/tchouangue/traj/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tchouangue/traj/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of $\texttt{traj}$ is to implement the three-step procedure proposed by Leffondree et al. (2004) to identify clusters of individual longitudinal trajectories. The procedure involves (1) calculating 24 measures describing the features of the trajectories; (2) using factor analysis to select a subset of the 24 measures and (3) using cluster analysis to identify clusters of trajectories, and classify each individual trajectory in one of the clusters.

## Installation

You can install the development version of $\texttt{traj}$ from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tchouangue/traj")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(traj)

# Step 1. Setup data 
data = example.data$data

# Step 2. Computing 24 measures of each trajectory
s1 = step1measures(data, ID=TRUE)

# Step 3. Factor analysis  
s2 = step2factors(s1)

# Step 4. Clustering the trajectories
s3 = step3clusters(s2, nclusters = 4)

plot(s3)

```

<!-- With a different database, make sure to well preprocess it in order to clean the data and if necessary, remove outliers. -->
